**The Role of Interoception and Theory of Mind in Deception**

### 2021-12-12 1_Measures.Rmd
minor edits
change social to interrogation

```{r warning=FALSE}
df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
  dplyr::filter(ID != 30) |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, instruction),
         condition = fct_recode(condition, "Interrogation" = "Social"),
         instruction = fct_relevel(instruction, "TRUTH")) |> 
  group_by(condition, instruction, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()

df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = instruction), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

@@

df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
sum(is.na(df$Confidence)) / nrow(df) * 100
df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
sum(is.na(df$HeartRate)) / nrow(df) * 100
df$RT[df$Participant == "S13"] <- NA # Slower than the others
df$RT[df$RT > 8.25] <- NA # Extreme RT values 
sum(is.na(df$RT)) / nrow(df) * 100
```

@@

```{r warning=FALSE}
df <- df |> 
  # Remove participants
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
  ungroup()
```

>>>>

```{r warning=FALSE}
df_physio <- read.csv("preprocessing/deceptiontask_physio_extracted.csv") |> 
  dplyr::filter(ID != 30) |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, Answer),
         instruction = fct_relevel(Answer, "TRUTH")) |> 
  group_by(condition, Answer, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()

df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  annotate("rect", xmin=1500, xmax=2500, ymin=-Inf, ymax=Inf, alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = Answer), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

@@

df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
df$RT[df$Participant == "S13"] <- NA # Slower than the others
df$RT[df$RT > 8.25] <- NA # Extreme RT values 
```

- Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100`
- Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100`
- Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100`

@@

```{r warning=FALSE}
df <- df |> 
  # Remove outlier trials
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
  ungroup()
```

### 2021-12-12 2_ManipulationChecks.Rmd
minor edits
change social to interrogation

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("HTT_")),
                 select(dfsub, starts_with("HCT_")), 
                 p_adjust = "none")

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_"), starts_with("HTT_")), 
                 p_adjust = "none")

@@

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant), data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant), data = df)

parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant), data = df)

parameters::parameters(model)
```

@@

## Effect of Condition

@@

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the social condition.
- Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?

@@

- Higher heart rate in lies vs. truths, and higher heart rate in social condition vs. polygraph.
- No interaction.

>>>>

```{r message=FALSE, warning=FALSE}
# Leave out HTT
# r <- correlation(select(dfsub, starts_with("HTT_")),
#                  select(dfsub, starts_with("HCT_")), 
#                  p_adjust = "none")
# 
# summary(r) |> 
#   plot()
```

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                        #starts_with("HTT_")), 
                 p_adjust = "none")

@@

summary(r) |> 
  plot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df)

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df)

@@

## Effect of Condition {.tabset}

@@

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the interrogation condition.
- Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?

@@

- Higher heart rate in lies vs. truths, and higher heart rate in interrogation condition vs. polygraph.
- No interaction.

### 2021-12-12 3_ToM.Rmd
minor edits
change social to interrogation

- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.

@@

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
    facet_wrap(~Answer)

@@

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
```

>>>>

- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in interrogation than polygraph condition.

@@

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) + 
    facet_wrap(~Answer)

@@

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
# p_conf_yoni_total
```

### 2021-12-12 index.Rmd
minor edits
change social to interrogation

---
title: '**The Place of Interoception and Theory of Mind in Deception**'
subtitle: A Subtitle
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
    df_print: default
    code_folding: hide
    code_download: yes
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: pygments
    toc: no
    toc_depth: 3
    df_print: kable
    number_sections: yes
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '2'
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---

@@

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(Participant = as.factor(paste0("S", Participant)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

>>>>

---
title: '**The Role of Interoception and Theory of Mind in Deception**'
subtitle: A Subtitle
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
    df_print: default
    code_folding: hide
    code_download: yes
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: pygments
    toc: no
    toc_depth: 3
    df_print: kable
    number_sections: yes
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '2'
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---

@@

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(Participant = factor(paste0("S", Participant), levels = paste0("S", 1:30)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

### 2021-12-12 preprocessing/data processing.Rmd
minor edits
change social to interrogation

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(trial = c(1:80),
           condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(Item = V1,
       Phrasing = V2,
       Answer = V3,
       Question = V4,
       social_start = V29,
       social_stop = V31,
       Confidence = V35,
       ConfidenceRT = V36,
       polyg_start = V43,
       polyg_stop = V45,
       ID = V47) %>%

  mutate(Confidence = as.numeric(Confidence),
         social_start = as.numeric(social_start),
         social_stop = as.numeric(social_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(RT = ifelse(condition == "Social", social_stop - social_start,
         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

>>>>

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(trial = c(1:80),
           condition = c(rep("Interrogation", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(Item = V1,
       Phrasing = V2,
       Answer = V3,
       Question = V4,
       interro_start = V29,
       interro_stop = V31,
       Confidence = V35,
       ConfidenceRT = V36,
       polyg_start = V43,
       polyg_stop = V45,
       ID = V47) %>%

  mutate(Confidence = as.numeric(Confidence),
         interro_start = as.numeric(interro_start),
         interro_stop = as.numeric(interro_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(RT = ifelse(condition == "Interrogation", interro_stop - interro_start,
         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%
